Distributions

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Working on figure for parameter space.

# Appendix figures

@@

**CP**

```{r fig.height=6}
cp.boot.fits %>% 
  filter(., dBIC == 0) %>% 
  dplyr::select(boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape)) +
  geom_point()
```

**PP**

```{r fig.height=6}
pp.boot.fits %>% 
  filter(., dBIC == 0) %>% 
  ggplot(., aes(y = estimate, x = fgroup)) +
  facet_wrap(dist~param, ncol = 2, scales = "free") +
  geom_boxplot()
```

**NP**

```{r fig.height=6}

np.boot.fits %>%
  filter(., dBIC == 0) %>% 
  dplyr::select(individual, boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) %>%
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = individual)) +
  geom_point() -> a

np.boot.fits %>%
  filter(., dBIC == 0) %>% 
  dplyr::select(individual, boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) %>%
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = individual)) +
  geom_point() -> b

np.boot.fits %>%
  filter(., dBIC == 0) %>% 
  dplyr::select(individual, boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = individual)) +
  geom_point() -> c

plot_grid(a, b, c)
```

@@

```{r fig.width=8, fig.height=6}
p1_angles <- ptpl %>% 
  drop_na(rel.angle) %>% 
  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360)) %>% 
  ggplot(., aes(x = d.angle)) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  labs(title = "Complete pooling")

>>>>

# Figure X - Best fit parameters

@@

cp.boot.fits %>%
  filter(., dBIC == 0) %>% 
  dplyr::select(boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) -> cp.best

pp.boot.fits %>%
  filter(., dBIC == 0) %>% 
  dplyr::select(group, boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) -> pp.best

np.boot.fits %>%
  filter(., dBIC == 0) %>% 
  dplyr::select(individual, boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) %>% 
  mutate(id = str_remove(individual, "B"), 
         group = case_when(
    id %in% c(1,3,5) ~ "G1",
    id %in% c(7) ~ "G2",
    id %in% c(13, 19) ~ "G3",
    id %in% c(22) ~ "G4",
    id %in% c(28) ~ "G5",
    id %in% c(49, 84) ~ "G6",
    id %in% c(29, 30) ~ "G7"
  )) %>%
  #slice_sample(., n = 100) %>% 
  arrange(group) %>% 
  group_by(group) %>% 
  mutate(shapeid = as.character(as.numeric(as.factor(individual)))) -> np.best
#View(np.best)

```{r FigureX, fig.height=12, fig.width=12}
library(MetBrewer)

colsx <- met.brewer("Gauguin", n = 7)
aval <- 0.3

figx.theme <- theme_bw() +
  theme(legend.position = "none")

cp.best %>% 
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog)) +
  geom_point(alpha = aval) +
  figx.theme -> cp.ln

cp.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape)) +
  geom_point(alpha = aval) +
  figx.theme -> cp.wei

cp.grid <- plot_grid(NULL, cp.ln, cp.wei, ncol = 3)

pp.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  figx.theme -> pp.gam

pp.best %>%
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  figx.theme -> pp.ln

pp.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  figx.theme -> pp.wei

pp.grid <- plot_grid(pp.gam, pp.ln, pp.wei, nrow = 1)

np.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  figx.theme -> np.gam

np.best %>% 
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  figx.theme -> np.ln

np.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  figx.theme -> np.wei

np.grid <- plot_grid(np.gam, np.ln, np.wei, nrow = 1)

plot_grid(cp.grid, pp.grid, np.grid, nrow = 3)
```

@@

```{r fig.width=8, fig.height=6, eval = FALSE}
p1_angles <- ptpl %>% 
  drop_na(rel.angle) %>% 
  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360)) %>% 
  ggplot(., aes(x = d.angle)) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  labs(title = "Complete pooling")
